Calculating Entropies With Nested Sampling

### 2017-02-08 paper/ms.tex
Final number
An abstract

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{}

% Keywords: add 3 to 10 keywords
\keyword{nested sampling; information theory; monte carlo}

@@

\begin{align}
H_{\d} &=% 945.42 \pm 1.02 \\ % 1000 mcmc steps
         % 929.26 \pm 1.00 \\ % 2000 mcmc steps
         % 927.40 \pm 0.98 \\ % 3000 mcmc steps
         % 927.26 \pm 1.00 \\ % 4000 mcmc steps
          928.21 \pm 1.00    % 5000 mcmc steps
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential entropy of
$p(\d)$ is $928.21 - 782.017 = 146.19 \pm 1.00$, consistent with the
true value of $146.499$.

>>>>

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{The Shannon entropy, and related quantities such as mutual
information, can be used to quantify uncertainty and relevance.
However, in practice, it can be difficult to compute these quantities
for arbitrary probability distributions, particularly if some probability
mass functions or densities cannot be evaluated. This paper introduces a
computational approach to evaluating entropies of probability distributions
that can be sampled. The method is based on Nested Sampling, and is related to Approximate Bayesian Computation. I demonstrate the method
on a simple gaussian example where the key quantities are known analytically,
and an experimental design example about scheduling observations in order
to measure the period of an oscillating signal.}

% Keywords: add 3 to 10 keywords
\keyword{information theory; entropy; mutual information; monte carlo;
nested sampling; bayesian inference}

@@

The result was
\begin{align}
H_{\d} &= 928.80 \pm 0.38.
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential entropy of
$p(\d)$ is $928.80 - 782.017 = 146.79 \pm 0.38$, consistent with the
true value of $146.499$.
